visualizemi: Visualization, Effect Size, and Replication of Measurement Invariance for Registered Reports

### 2024-03-08 appendix_7.Rmd
whew

```{r setup}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

@@

```{r echo = F}
boot.model.rs <- import("manu_data/boot.model.rs.appendix7.csv")
boot.model.rs
```

@@

```{r}
boot.partial.rs$boot_effects
```

@@

```{r}
boot.partial.rs$boot_summary
```

With the bootstrap summary, we see that no invariant intercept runs are found. Note that the `RS~1` does not calculate *d* because the *sd* is zero (thus, this would cause an error as *sd* is part of the denominator). The random runs also do not show a *d* score because the effect size is only calculated when at least 10% of the runs in `n_boot` or `n_random` are found. Since we only have 10 or 11 in that column, no effect size is calculated. The differences in the intercepts for the real data (`boot` columns) appear to be medium to large, showing *d* scores from 0.3 to 0.6. Therefore, we might expect that the English and Chinese samples have different average endorsement levels of the RS14.

>>>>

```{r setup}
knitr::opts_chunk$set(echo = TRUE, include = TRUE,
                      message = FALSE, warning = FALSE, size = "small")
```

@@

```{r echo = F}
boot.model.rs <- import("manu_data/boot.model.rs.appendix7.csv")
boot.model.rs %>% 
  dplyr::select(model, non_invariant, random_non_invariant, 
         h_nmi, h_nmi_p)
```

@@

```{r}
boot.partial.rs$boot_effects %>% 
  dplyr::select(term, non_invariant, random_non_invariant, 
         h_nmi, h_nmi_p)
```

@@

```{r}
boot.partial.rs$boot_summary %>% 
  dplyr::select(term, invariant, n_boot, d_boot)

boot.partial.rs$boot_summary %>% 
  dplyr::select(term, invariant, n_random, d_random)
```

With the bootstrap summary, we see that no invariant intercept runs are found (not all columns shown to save space). Note that the `RS~1` does not calculate *d* because the *sd* is zero (thus, this would cause an error as *sd* is part of the denominator). The random runs also do not show a *d* score because the effect size is only calculated when at least 10% of the runs in `n_boot` or `n_random` are found. Since we only have a few in that column, no effect size is calculated. The differences in the intercepts for the real data (`boot` columns) appear to be medium to large, showing *d* scores from 0.3 to 0.6. Therefore, we might expect that the English and Chinese samples have different average endorsement levels of the RS14.

### 2024-03-08 manuscript.Rmd
whew

```{r rs14-chinese-pic, include = T, fig.cap = "The differences in intercepts for the second item on the Rs14 by language sample. The differences between intercepts are shown on the left hand side with a clear separation between lines. The latent means also show a clear difference between groups where the English group appears to have lower scores overall than the Chinese group."}
knitr::include_graphics("figures/rs14-chinese-RS2.png")
```

```{r rs14-chinese-effect-pic, include = T, fig.cap = ""}
knitr::include_graphics("figures/rs14-chinese-effect_invariance_plot.png")
```

@@

```{r child = "appendix_7.Rmd"}

>>>>

```{r rs14-chinese-pic, include = T, fig.cap = "The differences in intercepts for the second item on the RS14 by language sample. The differences between intercepts are shown on the left hand side with a clear separation between lines. The latent means also show a clear difference between groups where the English group appears to have lower scores overall than the Chinese group."}
load("manu_data/fig-chinese-rs2.Rdata")
complete
```

```{r rs14-chinese-effect-pic, fig.width = 6, include = T, fig.cap = "Effect size differences for item intercepts on the English versus Chinese samples for the RS14.", warnings = FALSE, message = FALSE}
load("manu_data/boot.partial.rs.appendix7.Rdata")
effect_invariance_plot
```

@@

```{r child = "appendix_7.Rmd"}
```

### 2024-03-08 manuscript.tex
whew

\begin{figure}
\includegraphics[width=8in]{figures/rs14-chinese-RS2} \caption{The differences in intercepts for the second item on the Rs14 by language sample. The differences between intercepts are shown on the left hand side with a clear separation between lines. The latent means also show a clear difference between groups where the English group appears to have lower scores overall than the Chinese group.}\label{fig:rs14-chinese-pic}
\end{figure}

\begin{figure}
\includegraphics[width=8in]{figures/rs14-chinese-effect_invariance_plot} \end{figure}

@@

\begin{verbatim}
##        model non_invariant random_non_invariant    h_nmi      h_mi h_nmi_p
## 1 intercepts             1                    0 3.141593 -3.141593       1
##   h_mi_p
## 1     -1
\end{verbatim}

@@

\begin{verbatim}
## # A tibble: 15 x 7
##    term       non_invariant random_non_invariant h_nmi  h_mi h_nmi_p h_mi_p
##    <chr>              <dbl>                <dbl> <dbl> <dbl>   <dbl>  <dbl>
##  1 "RS ~1 "           0.991                0.007  2.78 -2.78   0.886 -0.886
##  2 "RS1 ~1 "          0.989                0.007  2.76 -2.76   0.880 -0.880
##  3 "RS10 ~1 "         0.988                0.007  2.75 -2.75   0.877 -0.877
##  4 "RS11 ~1 "         0.991                0.007  2.78 -2.78   0.886 -0.886
##  5 "RS12 ~1 "         0.991                0.007  2.78 -2.78   0.886 -0.886
##  6 "RS13 ~1 "         0.991                0.007  2.78 -2.78   0.886 -0.886
##  7 "RS14 ~1 "         0.99                 0.007  2.77 -2.77   0.883 -0.883
##  8 "RS2 ~1 "          0.985                0.007  2.73 -2.73   0.869 -0.869
##  9 "RS3 ~1 "          0.988                0.007  2.75 -2.75   0.877 -0.877
## 10 "RS4 ~1 "          0.99                 0.007  2.77 -2.77   0.883 -0.883
## 11 "RS5 ~1 "          0.984                0.007  2.72 -2.72   0.866 -0.866
## 12 "RS6 ~1 "          0.979                0.007  2.68 -2.68   0.854 -0.854
## 13 "RS7 ~1 "          0.974                0.007  2.65 -2.65   0.844 -0.844
## 14 "RS8 ~1 "          0.991                0.007  2.78 -2.78   0.886 -0.886
## 15 "RS9 ~1 "          0.987                0.007  2.75 -2.75   0.874 -0.874
\end{verbatim}

@@

\begin{verbatim}
## # A tibble: 30 x 26
## # Groups:   term, invariant [30]
##    term       invariant mean_boot_1 mean_boot_2 sd_boot_1 sd_boot_2
##    <chr>      <lgl>           <dbl>       <dbl>     <dbl>     <dbl>
##  1 "RS ~1 "   FALSE            0        -0.121      0        0.623 
##  2 "RS ~1 "   TRUE             0        -0.0110     0        0.680 
##  3 "RS1 ~1 "  FALSE            3.33      3.11       0.529    0.123 
##  4 "RS1 ~1 "  TRUE             3.34      3.07       0.550    0.112 
##  5 "RS10 ~1 " FALSE            3.35      3.01       0.740    0.286 
##  6 "RS10 ~1 " TRUE             3.37      2.95       0.725    0.268 
##  7 "RS11 ~1 " FALSE            2.88      2.70       0.489    0.0510
##  8 "RS11 ~1 " TRUE             2.79      2.68       0.528    0.0281
##  9 "RS12 ~1 " FALSE            3.42      3.12       0.657    0.197 
## 10 "RS12 ~1 " TRUE             3.30      3.08       0.733    0.183 
## # i 20 more rows
## # i 20 more variables: mean_boot_difference <dbl>, sd_boot_difference <dbl>,
## #   mean_boot_fit <dbl>, sd_boot_fit <dbl>, n_boot <int>, mean_random_1 <dbl>,
## #   mean_random_2 <dbl>, sd_random_1 <dbl>, sd_random_2 <dbl>,
## #   mean_random_difference <dbl>, sd_random_difference <dbl>,
## #   mean_random_fit <dbl>, sd_random_fit <dbl>, n_random <int>,
## #   d_boot_low <dbl>, d_boot <dbl>, d_boot_high <dbl>, d_random_low <dbl>, ...
\end{verbatim}

With the bootstrap summary, we see that no invariant intercept runs are found. Note that the \texttt{RS\textasciitilde{}1} does not calculate \emph{d} because the \emph{sd} is zero (thus, this would cause an error as \emph{sd} is part of the denominator). The random runs also do not show a \emph{d} score because the effect size is only calculated when at least 10\% of the runs in \texttt{n\_boot} or \texttt{n\_random} are found. Since we only have 10 or 11 in that column, no effect size is calculated. The differences in the intercepts for the real data (\texttt{boot} columns) appear to be medium to large, showing \emph{d} scores from 0.3 to 0.6. Therefore, we might expect that the English and Chinese samples have different average endorsement levels of the RS14.

>>>>

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/rs14-chinese-pic-1.pdf}
\caption{\label{fig:rs14-chinese-pic}The differences in intercepts for the second item on the RS14 by language sample. The differences between intercepts are shown on the left hand side with a clear separation between lines. The latent means also show a clear difference between groups where the English group appears to have lower scores overall than the Chinese group.}
\end{figure}

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/rs14-chinese-effect-pic-1.pdf}
\caption{\label{fig:rs14-chinese-effect-pic}Effect size differences for item intercepts on the English versus Chinese samples for the RS14.}
\end{figure}

@@

\begin{verbatim}
##        model non_invariant random_non_invariant    h_nmi h_nmi_p
## 1 intercepts             1                    0 3.141593       1
\end{verbatim}

@@

\begin{verbatim}
##        term non_invariant random_non_invariant    h_nmi  h_nmi_p
## 1    RS ~1              1                0.002 3.052120 0.971520
## 2   RS1 ~1              1                0.001 3.078337 0.979865
## 3  RS10 ~1              1                0.002 3.052120 0.971520
## 4  RS11 ~1              1                0.002 3.052120 0.971520
## 5  RS12 ~1              1                0.002 3.052120 0.971520
## 6  RS13 ~1              1                0.002 3.052120 0.971520
## 7  RS14 ~1              1                0.002 3.052120 0.971520
## 8   RS2 ~1              1                0.002 3.052120 0.971520
## 9   RS3 ~1              1                0.002 3.052120 0.971520
## 10  RS4 ~1              1                0.002 3.052120 0.971520
## 11  RS5 ~1              1                0.002 3.052120 0.971520
## 12  RS6 ~1              1                0.002 3.052120 0.971520
## 13  RS7 ~1              1                0.001 3.078337 0.979865
## 14  RS8 ~1              1                0.002 3.052120 0.971520
## 15  RS9 ~1              1                0.002 3.052120 0.971520
\end{verbatim}

@@

\begin{verbatim}
##        term invariant n_boot     d_boot
## 1    RS ~1      FALSE   1000         NA
## 2   RS1 ~1      FALSE   1000  0.2913872
## 3  RS10 ~1      FALSE   1000  0.3596961
## 4  RS11 ~1      FALSE   1000 -0.6589317
## 5  RS12 ~1      FALSE   1000 -0.3010202
## 6  RS13 ~1      FALSE   1000 -0.4005088
## 7  RS14 ~1      FALSE   1000 -0.5665988
## 8   RS2 ~1      FALSE   1000 -0.5540349
## 9   RS3 ~1      FALSE   1000 -0.6218628
## 10  RS4 ~1      FALSE   1000 -0.6245830
## 11  RS5 ~1      FALSE   1000 -0.3334520
## 12  RS6 ~1      FALSE   1000 -0.5014247
## 13  RS7 ~1      FALSE   1000 -0.2381644
## 14  RS8 ~1      FALSE   1000 -0.6333750
## 15  RS9 ~1      FALSE   1000 -0.5986866
\end{verbatim}

\begin{verbatim}
##        term invariant n_random d_random
## 1    RS ~1      FALSE        2       NA
## 2   RS1 ~1      FALSE        1       NA
## 3  RS10 ~1      FALSE        2       NA
## 4  RS11 ~1      FALSE        2       NA
## 5  RS12 ~1      FALSE        2       NA
## 6  RS13 ~1      FALSE        2       NA
## 7  RS14 ~1      FALSE        2       NA
## 8   RS2 ~1      FALSE        2       NA
## 9   RS3 ~1      FALSE        2       NA
## 10  RS4 ~1      FALSE        2       NA
## 11  RS5 ~1      FALSE        2       NA
## 12  RS6 ~1      FALSE        2       NA
## 13  RS7 ~1      FALSE        1       NA
## 14  RS8 ~1      FALSE        2       NA
## 15  RS9 ~1      FALSE        2       NA
\end{verbatim}

With the bootstrap summary, we see that no invariant intercept runs are found (not all columns shown to save space). Note that the \texttt{RS\textasciitilde{}1} does not calculate \emph{d} because the \emph{sd} is zero (thus, this would cause an error as \emph{sd} is part of the denominator). The random runs also do not show a \emph{d} score because the effect size is only calculated when at least 10\% of the runs in \texttt{n\_boot} or \texttt{n\_random} are found. Since we only have a few in that column, no effect size is calculated. The differences in the intercepts for the real data (\texttt{boot} columns) appear to be medium to large, showing \emph{d} scores from 0.3 to 0.6. Therefore, we might expect that the English and Chinese samples have different average endorsement levels of the RS14.
